---
title: "Assessment III: Sports Analytics Jan Plan"
name: ""
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_chunk$set(warning = FALSE)
knitr::opts_chunk$set(message = FALSE)
```

##### 1. Load packages and read in the 2018 NCAA football rushing data
```{r}
# load the tidyverse 

# the data is stored here: https://raw.githubusercontent.com/majerus/Sports_Analytics_Course/master/college_rushing_data_2018.csv


```

##### 2. Explore the rushing data using the glimpse function
```{r}

```

##### 3. Which conferences are included in the data? 
```{r}


```


##### 4. Which conference has the most rushing yards in the data? 
```{r}


```

##### 5. Create a new data frame called `top100` that contains only the top 100 rushers from 2018. 
```{r}


```

##### 6. Create a new variable in `top100` called `ave` that calculates each rushers average yards per carry.  
```{r}


```

##### 7. Which conference has the most rushers in the top 100?
```{r}


```

##### 8. Create a scatter plot of yards vs. touchdowns for the top 100 rushers.  
```{r}


```

##### 9. Use the Top 100 Rushers data to create a bar graph of total yards for each conference.   
```{r}


```

##### 10. Who are the top 100 rushers in the conference with the most total rushing yards?  
```{r}


```
