---
title: "Assessment I: Sports Analytics Jan Plan"
name: ""
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Section 1: Loading Packages and Data

##### 1. Load the tidyverse library
```{r}
```

##### 2. Load the Olympic medals data into a data frame called olympics

```{r, echo=FALSE}
# the data is stored here: https://raw.githubusercontent.com/majerus/Sports_Analytics_Course/master/olympics.csv



```

Here's some info about variables in the data: 

- ID - Unique number for each athlete
- Name - Athlete's name
- Sex - M or F
- Age - Integer
- Height - In centimeters
- Weight - In kilograms
- Team - Team name
- NOC - National Olympic Committee 3-letter code
- Games - Year and season
- Year - Integer
- Season - Summer or Winter
- City - Host city
- Sport - Sport
- Event - Event
- Medal - Gold, Silver, Bronze, or NA

## Section 2: Describing the data

##### 3. How many rows are in the data? 

##### 4. How many columns are in the data?



## Section 3: Country (NOC) Medal Counts

##### 5. Which country (NOC) has won the most medals?  
```{r}

```

##### 6. Which country has won the most medals in the winter games? 
```{r}

```

## Section 4: Sport Medal Counts

##### 7. Which sport has awarded the fewest medals? 
```{r}

```

##### 8. In how many Olympic Games were medals awarded in the sport of Tug-Of-War?
```{r}

```


## Section 5: BMI

#####  9. Which gold medal winner has the highest BMI? (BMI = kg/m^2)
```{r}

```


## Section 6: Graphing

##### 10. Create a box of the age of medal winners by sex
```{r}

```

##### 11. Who is that person who won a medal when they were 10? 
```{r}

```

##### 12. Facet the boxplot by Medal
```{r}

```


## Section 7: Bonus 

##### Which cities have hosted the games multiple times?
```{r}

```


