---
title: "Assessment II: Sports Analytics Jan Plan"
name: ""
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_chunk$set(warning = FALSE)
knitr::opts_chunk$set(message = FALSE)
```

##### 1. Load packages and read in the goalie data
```{r}
# load tidyverse and plotly


# the data is stored here: https://raw.githubusercontent.com/majerus/Sports_Analytics_Course/master/hockey_goalie_data.csv

# read in hockey goalie data into a data frame called goalies


```

Here's some info about variables in the data: 

- playerID: Player ID
- tmID: Team ID
- year: Year (2005-06 listed as "2005")
- stint: Stint (order of appearance in a season)
- GP: Games played
- Min: Minutes
- W: Wins
- L: Losses
- T_OL: Ties / overtime losses
- SHO: Shutouts
- GA: Goals against
- SA: Shots against
- firstName: First name
- lastName: Last name
- height: Height in inches
- weight: Weight in pounds
- birthCountry: Country of birth

##### 2. Explore the hockey data using the glimpse function
```{r}

```

##### 3. Which hockey leagues does the data cover? 
```{r}


```


##### 4. Create a new data frame called `nhl` that contains only seasons that were played in the NHL. This data will be used for all of the following questions. 
```{r}


```


##### 5. Create a new variable in `nhl` called `name` that combines the first name and last name columns into a single column. 

```{r}
# hint the paste function may be helpful. 

```

##### 6. Which goalie has played the most games their NHL career?
```{r}


```

##### 7. What is the highest save percentage for a goalie playing 20 games or more in a season?
```{r}
# Note - save percentage is the number of saves divided by the number of shots on goal. You will need to calculate the number of saves.

```

##### 8. Create a scatter plot of save percentage over time for goalies who played more than 20 games in a season. 
```{r}
# Note year should be on the x-axis 
# Note exclude seasons prior to 1980 


```

##### 9. Make your scatter plot interactive using plotly.  
```{r}

```

##### 10. Who is that goalie with the lowest save percentage in 2006?  
```{r}



```

