---
title: "Assessment I: Sports Analytics Jan Plan"
name: ""
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_chunk$set(warning = FALSE)
knitr::opts_chunk$set(message = FALSE)
```

## Section 1: Loading Packages and Data

##### 1. Load the tidyverse library
```{r, message=FALSE, warning=FALSE}
library(tidyverse)
```

##### 2. Load the Olympic medals data into a data frame called olympics

```{r, echo=TRUE, message=FALSE}
# the data is stored here: https://raw.githubusercontent.com/majerus/Sports_Analytics_Course/master/olympics.csv

olympics <- read_csv("https://raw.githubusercontent.com/majerus/Sports_Analytics_Course/master/olympics.csv")



```

Here's some info about variables in the data: 

- ID - Unique number for each athlete
- Name - Athlete's name
- Sex - M or F
- Age - Integer
- Height - In centimeters
- Weight - In kilograms
- Team - Team name
- NOC - National Olympic Committee 3-letter code
- Games - Year and season
- Year - Integer
- Season - Summer or Winter
- City - Host city
- Sport - Sport
- Event - Event
- Medal - Gold, Silver, Bronze, or NA

## Section 2: Describing the data

##### 3. How many rows are in the data? 

There are `r nrow(olympics)` in the data. 

##### 4. How many columns are in the data?

There are `r ncol(olympics)` in the data. 

## Section 3: Country (NOC) Medal Counts

##### 5. Which country (NOC) has won the most medals?  
```{r}
olympics %>% 
  count(NOC) %>% 
  arrange(desc(n)) %>% 
  slice(1)
```

The USA has won the most medals. 

##### 6. Which country has won the most medals in the winter games? 
```{r}
olympics %>% 
  filter(Season == "Winter") %>% 
  count(NOC) %>% 
  arrange(desc(n)) %>% 
  slice(1)
```

The USA has won the most medals in the Winter Olympics. 

## Section 4: Sport Medal Counts

##### 7. Which sport has awarded the fewest medals? 
```{r}

olympics %>% 
  count(Sport) %>% 
  arrange(n) %>% 
  slice(1)

```
Aeronautics has awarded only a single medal. 

##### 8. In how many Olympic Games were medals awarded in the sport of Tug-Of-War?
```{r}
olympics %>% 
  filter(Sport == "Tug-Of-War") %>% 
  distinct(Games) %>% 
  nrow()
```
Medals were awarded in Tug-Of-War in 6 Olympics. 

## Section 5: BMI

#####  9. Which gold medal winner has the highest BMI? (BMI = kg/m^2)
```{r}
olympics %>% 
  filter(Medal == "Gold") %>% 
  mutate(height_meters = Height/100,
         height_meters_sq = height_meters^2,
         bmi = Weight/height_meters_sq) %>% 
  arrange(desc(bmi)) %>% 
  select(Name, Games, Sport, Weight, Height, bmi) %>%  
  slice(1) 
```
Andrey Ivanovich Chemerkin has the highest bmi of all gold medal winners. He won gold in weightlight during the 1996 summer games. 

## Section 6: Graphing

##### 10. Create a box plot of the age of medal winners by sex
```{r}
olympics %>% 
  ggplot(., aes(x = Sex, y = Age)) +
  geom_boxplot()
```

##### 11. Who is that person who won a medal when they were 10? 
```{r}
olympics %>% 
  filter(Age == 10) %>% 
  select(Name, Age, NOC, Sport, Games, Medal)
```
Dimitrios Loudras won a bronze medal in the 1896 Summer Olympics in gymnastics at the age of 10. 

##### 12. Facet the boxplot by Medal
```{r}
olympics %>% 
  ggplot(., aes(x = Sex, y = Age)) +
  geom_boxplot() + 
  facet_wrap(~Medal)

```


## Section 7: Bonus 

##### Which cities have hosted the games multiple times?
```{r}

olympics %>% 
  select(City, Games) %>% 
  distinct() %>% 
  count(City) %>% 
  filter(n > 1)

```
Eight cities have hosted the Olympics more than once. There are Athina, Innsbruck, Lake Placid, London, Los Angeles, Paris, Sankt Moritz, and Stockholm. 

